Supporting Information

### 2015-08-14 ms.Rmd
test effect of increasing # of genes sent for clustering on hypergeom tests

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("cairo_pdf"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=TRUE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

```{r mfuzz}
figCount <- incCount(figCount, "f_mfuzzClusters")
```

@@

To understand the contents of the clusters, **z-score for each tf family by cluster**.

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.height=4.40933, cache = FALSE}
print(f_mfuzzClusters)
```

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("cairo_pdf"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

```{r mfuzz}
figCount <- incCount(figCount, "f_mfuzzClusters")
tableCount <- incCount(tableCount, "t_hypergeom")
t_hypergeom <- readRDS('output/mfuzz/sigFamilies.Rds')
# fix p-values
t_hypergeom[,grepl("^\\*p", colnames(t_hypergeom))] <- gsub("e-(\\d+)", "x10^-\\1^",
format.pval(t_hypergeom[,grepl("^\\*p", colnames(t_hypergeom))], digits = 2,
            na.form = ""))
t_hypergeom[is.na(t_hypergeom)] <- ""
```

@@

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.height=4.40933}
print(f_mfuzzClusters)
```

After examining the lists of genes in each cluster it was evident that most clusters had an enrichment of transcription factors (**tables in SI**). To determine whether particular TF families were associated with particular patterns of expression, the enrichment of TF family members in each cluster was calculated using hypergeometric tests. These calculations were carried out for families that had two or more members in any given cluster (**`r I(pasteLabel("Table", tableCount, "t_hypergeom"))`**). After adjustment for multiple comparisons,   MADS genes were significantly over-represented in clusters 1 and 4, both of which contain genes that have higher expression in later meristem samples. ABI3VP transcription factors are

<a id="t_hypergeom"></a>
```{r hypergeom, results = "markup"}
knitr::kable(t_hypergeom, caption = 'Transcription factor family enrichment per cluster', align = 'r')
```

Hypergeometric tests were performed for each cluster that contained more than one member of a particular TF family to calculate the probability of observing the corresponding

### 2015-08-14 si.Rmd
test effect of increasing # of genes sent for clustering on hypergeom tests

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---

>>>>

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---
